---
title: "Boston Housing Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Boston Housing Partial Dependence Plot

First, get dataset.

```{r}
library("pdp")
boston <- read.csv("C://Users//user//Desktop//다변량//BostonHousing.csv")
colnames(boston) <- c("CRIM", "ZN","INDUS", "CHAS","NOX", "RM",
                      "AGE", "DIS", "RAD", "TAX", "PTRATIO", "B", "LSTAT", "MEDV")
```

Response Variable: MEDV

Data violate many assumptions(linearity, normality, constant variance)

# Simple linear regression(Harrison and Rubinfeld(1978))
```{r}
boston$B <- boston$B-0.63
attach(boston)
lm_boston <- lm(log(MEDV) ~ RM^2+AGE+log(DIS)+log(RAD)+TAX+PTRATIO+B^2+log(LSTAT)+CRIM+ZN+INDUS+CHAS+NOX^2)
summary(lm_boston) #R-squared: 0.8035
detach(boston)
```
PDPs are useful for visualizing the relationships discovered by complex machine learning algorithms

Two most important functions exported by pdp are: "partial", "plotPartial"

development ver: https://github.com/bgreenwell/pdp

supported models include:: Decision tree, Bagged decision trees, Boosted decision trees, Linear model, Multivariate adaptive regression splines, Random forest, Support vector machine , ...

## Random Forest
```{r}
library(randomForest)
set.seed(101) # for reproducibility
boston.rf <- randomForest(MEDV ~ ., data = boston, importance = TRUE)
boston.rf
varImpPlot(boston.rf) # Importance scores
```

percentage of lower status of the population(LSTAT) and average number of rooms per dwelling(RM) are highly associated with MEDV. Drawing partial dependence plot of MEDV on LSTAT, RM might help understanding nature of these associations.

```{r}
partialPlot(boston.rf, pred.data = boston, x.var = "LSTAT")
#partial plot uses lattice graphic, so use print.lattice function
library("UsingR")
par(mfrow=c(1,2))
# Left: default plot based on Random Forest
print(partial(boston.rf, pred.var = "LSTAT", plot = TRUE), position = c(0, 0, 0.5, 1), more = TRUE)
# Right: adds LOESS smooth
print(boston.rf %>% partial(pred.var = "LSTAT") %>%
  plotPartial(smooth = TRUE, lwd = 2, ylab = expression(f(LSTAT))), position = c(0.5, 0, 1, 1))
```

```{r}
# Compute partial dependence data for LSTAT and RM
pd <- partial(boston.rf, pred.var = c("LSTAT", "RM"))

# Add contour lines and use a different color palette
col <- colorRampPalette(c("coral1", "firebrick1", "gray0"))
boston_contour <- plotPartial(pd, contour = TRUE, col.regions = col)

# 3-D surface
boston_3d <- plotPartial(pd, levelplot = FALSE, zlab = "cmedv", drape = TRUE,
                    colorkey = TRUE, screen = list(z = -20, x = -60))
# Contour lines
grid.arrange(boston_contour, boston_3d, ncol = 2)
```